Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
shrinking space after images
more space savings

\begin{figure}[t!]
\centering
\includegraphics[width=.75\columnwidth]{figures/pipeline}
\caption{Compilation pipeline stages for Propane.}
\label{fig:pipeline}
\end{figure}

@@

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
\end{figure*}

@@

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
  \label{fig:example-compilation}
\end{figure*}

@@

The checks for failure safety described above overlook one critical point: Paths for a higher preference might not actually exist due to loops. To avoid this situation, the compiler conservatively checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR. 
%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

\subsection{Abstract BGP}

@@

\begin{figure}[t!]
%% \begin{lstlisting}[frame=single, mathescape=true]
%% $\Router{A}$
%%   Match $\PEER=C, \COMM=(3,2)$
%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
%% $\Router{B}$
%%   Match $\PEER = C, \COMM = (-,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%%   Match $\PEER = C, \COMM = (3,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%% $\Router{C}$
%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
%%   Match $\PEER = D, \COMM = (2,2)$
%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
%% $\Router{D}$
%%   Match $\REGEX{X + Y}$
%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
%% $\Router{E}$
%%   Match $\REGEX{Z}$
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
%% \end{lstlisting}
\begin{code}
\Router{A}
  Match \PEER=C, \COMM=(3,2)
    Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
\Router{B}
  Match \PEER = C, \COMM = (-,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
  Match \PEER = C, \COMM = (3,2)
    Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
           \MED \Arrow 81, \PEER \Arrow W
\Router{C}
  Match[LP=99] \PEER = E, \COMM = (-,2) 
    Export \COMM \Arrow (-,2), \PEER \Arrow B
  Match \PEER = D, \COMM = (2,2)
    Export \COMM \Arrow (3,2), \PEER \Arrow A,B
\Router{D}
  Match \REGEX{X + Y}
    Export \COMM \Arrow (2,2), \PEER \Arrow C
\Router{E}
  Match \REGEX{Z}
    Export \COMM \Arrow (-,2), \PEER \Arrow C
\end{code}\vspace{-.5cm}
\caption{Abstract BGP router configurations. \label{fig:abgp-config}}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=.75\columnwidth]{figures/pipeline}
  \caption{Compilation pipeline stages for Propane.}
  \label{fig:pipeline}
  \vspace{-1em}
\end{figure}

@@

  \caption{Regular Intermediate Language (RIL) syntax (left), and
           Propane language expansions (right).}
  \label{fig:rir-syntax}
  \vspace{-1em}
\end{figure*}

@@

  \caption{Example Product Graph IR construction for policy: $(\CD{W} \cdot \CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \Out) \Prefer (\CD{W} \cdot \CD{B} \cdot \In^* \cdot \Out)$.}
  \label{fig:example-compilation}
  \vspace{-1em}
\end{figure*}

@@

The checks for failure safety described above overlook one critical point: Paths for a higher preference might not exist due to loops. To avoid this situation, the compiler checks that, when node $x$ protects against failures for node $y$, its does so without using any nodes that shadow another node that appears ``above'' $x$ in the PGIR. 
%It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.
%even if the analysis determines that a node $x$ protects against failures of another node $y$, it may be tricked into thinking $x$ has a particular path that will actually be discarded by BGP's loop prevention mechanism due to locations previously traversed before arriving at $x$. To avoid this situation, the compiler conservatively checks that $x$ protects against $y$ without using any nodes that shadow another node that appears above $x$ in the PGIR (i.e., nodes reachable from $x$ in $G_j^R$). It is fine however, to reuse the same nodes that appear above $x$, since any path that went through another node $z$ to get to $x$, but then looped through $z$ again, would be obtainable from $z$ itself.

\para{Aggregation-Induced Black Holes}
Because the \sysname compiler has the complete user policy and topology, it is also able to efficiently check that user-specified aggregates do not black hole traffic for up to $k$ failures, where $k$ is specified by the user. The algorithm for aggregation failure safety is detailed in Section~\ref{sec:black-holes} of the appendix.
\subsection{Abstract BGP}

@@

\begin{figure}[t!]
%% \begin{lstlisting}[frame=single, mathescape=true]
%% $\Router{A}$
%%   Match $\PEER=C, \COMM=(3,2)$
%%     Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
%% $\Router{B}$
%%   Match $\PEER = C, \COMM = (-,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%%   Match $\PEER = C, \COMM = (3,2)$
%%     Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
%%            $\MED \leftarrow 81, \PEER \leftarrow W$
%% $\Router{C}$
%%   Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
%%   Match $\PEER = D, \COMM = (2,2)$
%%     Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
%% $\Router{D}$
%%   Match $\REGEX{X + Y}$
%%     Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
%% $\Router{E}$
%%   Match $\REGEX{Z}$
%%     Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
%% \end{lstlisting}
\begin{code}
  \Router{A}
    Match \PEER=C, \COMM=(3,2)
      Export \COMM \Arrow (4,2), \MED \Arrow 80, \PEER \Arrow W
  \Router{B}
    Match \PEER = C, \COMM = (-,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
    Match \PEER = C, \COMM = (3,2)
      Export \COMM \Arrow (-,3), \COMM \Arrow \text{noexport},
             \MED \Arrow 81, \PEER \Arrow W
  \Router{C}
    Match[LP=99] \PEER = E, \COMM = (-,2) 
      Export \COMM \Arrow (-,2), \PEER \Arrow B
    Match \PEER = D, \COMM = (2,2)
      Export \COMM \Arrow (3,2), \PEER \Arrow A,B
  \Router{D}
    Match \REGEX{X + Y}
      Export \COMM \Arrow (2,2), \PEER \Arrow C
  \Router{E}
    Match \REGEX{Z}
      Export \COMM \Arrow (-,2), \PEER \Arrow C
  \end{code}
  \vspace{-2em} 
  \caption{Abstract BGP router configurations. \label{fig:abgp-config}}
  \vspace{-1em}
\end{figure}

### 2016-01-29 paper/evaluation.tex
adding appendix
shrinking space after images
more space savings

@@

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \caption{Compilation time. \label{fig:compilation-times}}
\end{figure}

@@

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
\end{figure}

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix since the \sysname compiler can compile for each prefix independently, and in parallel. At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

@@

$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter topology, whereas \sysname selectively imported the route only below a certain tier;
%\sysname could use a similar implementation mechanism in the future as an optimization.

>>>>

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \caption{Compilation time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

@@

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel. At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

@@

$i)$ operators used the no-export community to prevent routes from leaking beyond a certain tier of the datacenter, while \sysname selectively imported the route only below the tier;
%\sysname could use a similar implementation mechanism in the future as an optimization.

### 2016-01-29 paper/motivation.tex
shrinking space after images
more space savings

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/example1}
\caption{Creating router-level policies is difficult.}
\label{fig:example1}
\end{figure}

@@

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. % Implementing P2 properly will require MEDs to be
% appropriately configured. 
\todd{I commented out the sentence about MEDs for P2, because the next
  two sentences seem to be about P2 instead of P3 and P4, which it
  originally said.  Please check}  To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/example2}
\caption{Policy-compliance under failures is difficult.}
\label{fig:example2}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example1}
  \caption{Creating router-level policies is difficult.}
  \label{fig:example1}
  \vspace{-1em}
\end{figure}

@@

To implement P1 of the policy, the operators must compute and assign
local preferences such that preferences at \CD{Cust}-facing interfaces
$>$ \CD{Peer}-facing interfaces $>$ \CD{Prov}-facing interfaces. At
the same time, to satisfy P3 the preference at \CD{R2}'s
\CD{Cust}-facing interface should be lower than that at
\CD{R1}. Implementing P3 properly will require MEDs to be appropriately configured. 
To implement P2, the operators can assign communities that
indicate where a certain routing announcement entered the
network. Then, \CD{R4} must be configured to not announce to
$\CD{Peer}$ routes that have communities that correspond to the
\CD{R2}-\CD{Prov} link but to announce routes with communities for the \CD{R2}-\CD{Cust} and \CD{R1}-\CD{Cust} links. Finally, to implement P4 and P5, the operators will have to compute and configure appropriate prefix- and AS-path-based filters at each router.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/example2}
  \caption{Policy-compliance under failures is difficult.}
  \label{fig:example2}
  \vspace{-1em}
\end{figure}
